Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-24 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Made corrections and added new images

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. This situation is often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation. 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  These maps identify different types of targets. 
  We show that our proposal outperforms its competitors using simulated and SAR data.
# ACF Which is "our proposal" and which are the "competitors"?
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  Not applicable.
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article is fully reproducible using RMarkdown. All code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 12 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

@@

source("../Code/R/MainFunctions/van_es_estimator.R")
source("../Code/R/MainFunctions/correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/vasicek_estimator.R")
source("../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../Code/R/Programs/read_ENVI_images.R")

@@

Our work aims to improve the identification of potential roughness features in SAR intensity data.
<!-- ACF The following sentence is misleading: the gamma law is a consequence of infinitely many backscatterers with none dominating the return, not the other way aroud. Rephrase. -->
Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully-developed speckle and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.

@@

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications. The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
We study two ways of estimating the coefficient of variation.

@@

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
Correa&nbsp;\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
Ebrahimi et al&nbsp;\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
<!-- ACF Define the estimators and state their main properties -->

@@

We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples from the \(G_I^0\) law of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different mean, number of looks and roughness. 
We present the results with
\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). 
The results are consistent with the other situations. 
We used $B=100$ bootstrap samples and the heuristic spacing
\(m=\left[\sqrt{n}+0.5\right]\), as recommended in the literature.

@@

# Number of replications
R <-300

# Number of bootstrap replications
B1 <- 20
mu_values <- c(1, 10)
alpha <- -20
L <- 5

@@

# Define estimators
estimators_to_table <- c( "Al Omari","Correa", "Ebrahimi", "Al Omari Bootstrap",  "Correa Bootstrap","Ebrahimi Bootstrap")

@@

colnames(reshaped_results) <- c("$\\mu$", "$n$", "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$",  "$\\widehat{H}_{\\text{AO}}$", "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$")

@@

We explore a robust alternative to CV, as described by \citet{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
scale and location, respectively. The sample version for the MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
is an estimate for the median of the population, which can be approximated by the median of the sample.

@@

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
<!-- ACF This is an important contribution. Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close. Therefore, their difference should be small. Explain why you need \widebar{Z} -->
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

R <- 2000
mu <- 1
B <- 2

@@

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      #z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_H$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
In all cases, the nominal level was achieved. 
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.
<!-- ACF Please clarify which alternatives you used for the power -->

@@

  return(p_value < alpha_nominal)  
}
R <- 1000
mu <- 1
B <- 1
L_values <- c( 3, 5, 8, 11)
sample_sizes <- c( 25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results <- data.frame()
for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

@@

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

@@

        for (r in 1:R) {
          z <- gi0_sample(mu, -5, L, s)
          TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        }

@@

  return(results)
}
R <- 1000
mu <- 1
L_values <- c(3, 5,  8, 11)
B <- 1
sample_sizes <- c(25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")
```

@@

The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
\textcolor{green}{%
It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.
}

\textcolor{red}{%
ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião. Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica. Uma alternativa empírica para uma solução do momento usando distribuições mais desenvolvidas na literatura e que sejam analiticamente tratáveis. Estou pensando corretamente? Se sim, por que não log-t-student, log-Laplace, power exponential, Log-hyperbolic,.... (e a lista segue). Sugiro talvez indicar (i) a dedução da distribuição assintótica das estatísticas em função de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro. Do que eu entendi, a suposição da normal assintótica para entropia vem de uma coleção de trabalhos teóricos. Já a LN, do que percebi, não. Coloquei um comentário em verde. Vejam se estão de acordo.
}

@@

# Graficar las comparaciones
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlab = "CV")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","#FDA75F"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

## SAR Data

>>>>

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. This situation is often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation (CV). 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  Finally, we show that our proposal, the entropy-based test, outperforms existing methods such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
#These maps identify different types of targets.
# We show that our proposal outperforms its competitors using simulated and SAR data.
# ACF Which is "our proposal" and which are the "competitors"? # ok
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  The author J.A. would like to thank the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE) for their support. 
authorcontributions: |
  All authors (A.C.F., J.A, and A.D.C.N.) discussed the results and contributed to the research. All authors have read and agreed to the published version of the manuscript.

funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 24 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

@@

source("../Code/R/MainFunctions/van_es_estimator.R")
source("../Code/R/MainFunctions/correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../Code/R/MainFunctions/ebrahimi_estimator.R")
#source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/vasicek_estimator.R")
source("../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
#source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../Code/R/Programs/read_ENVI_images.R")

@@

Our work aims to improve the identification of potential roughness features in SAR intensity data.
<!-- ACF The following sentence is misleading: the gamma law is a consequence of infinitely many backscatterers with none dominating the return, not the other way aroud. Rephrase. -->
<!-- JA Corrected -->
Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions

@@

The CV, introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications. The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
We study two ways of estimating the coefficient of variation.

@@

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}.

* Correa&nbsp;\cite{correa1995new}:
\begin{equation}
\widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \log \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\widebar{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\widebar{Z}_{(i)}\right)^2},
\end{equation}
where  $\widebar{Z}_{(i)}=(2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}$, $m< \frac{n}{2}$, $Z_{(i)}=Z_{(1)}$ for $i<1$ and $Z_{(i)}=Z_{(n)}$ for $i>n$. Based on simulation, he showed that his estimator has a smaller mean square error in comparison with Vasicek's approach.

* Ebrahimi et al.&nbsp;\cite{Ebrahimi1994}:
\begin{equation}
\widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
\end{equation}
where
$$
c_i=\begin{cases}1+(i-1) / m & \text { if } \quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m,\\ 1+(n-i) / m & \text { if }\quad n-m+1 \leq i \leq n.\end{cases}
$$
The authors proved that $\widehat{H}_{\text{E}}(\bm{Z})\xrightarrow{p}H[Z]$, when $m,n\rightarrow\infty$ and  $m/n\rightarrow0$.

* Al-Omari&nbsp;\cite{IbrahimAlOmari2014}:
$$
\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right]
$$
where
$$
\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
$$
in which $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$, and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.

@@

We analyzed the performance of these estimators with a Monte Carlo study: \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\), with
\(\mu\in\left\{1, 10\right\}\) and \(L=5\). 
The results are consistent with the other situations. 
We used $B=200$ bootstrap samples and the heuristic spacing
\(m=\left[\sqrt{n}+0.5\right]\), as recommended in the literature.

@@

# Number of replications
R <-500

# Number of bootstrap replications
B1 <- 30
mu_values <- c(1, 10)
alpha <- -50
L <- 5

@@

# Define estimators
estimators_to_table <- c( "Correa", "Ebrahimi", "Al Omari", "Correa Bootstrap","Ebrahimi Bootstrap","Al Omari Bootstrap")

@@

colnames(reshaped_results) <- c("$\\mu$", "$n$",  "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$",  "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$",   "$\\widehat{H}_{\\text{C}}$", "$\\widehat{H}_{\\text{E}}$","$\\widehat{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$","$\\widetilde{H}_{\\text{AO}}$")

@@

We explore a robust alternative to CV, as describedby&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
scale and location, respectively. 
The sample version for the MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
is an estimate for the median of the population, which can be approximated by the median of the sample.

@@

For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed. It is based on an  empirical distribution that arises  from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of Gamma SAR&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L_0\geq 1$ is known.

Hence, the entropy-based test statistic is defined as:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
\end{equation}

This test statistic  aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L_0)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution would shift from zero, suggesting significant differences and implying the presence of heterogeneous clutter.

<!-- ACF This is an important contribution. Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close. Therefore, their difference should be small. Explain why you need \widebar{Z} -->
<!-- JA Corrected -->

Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes using \(\widetilde{H}_{\text{AO}}\) estimator, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

R <- 2000
mu <- 1
B <- 50

@@

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      #z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
      #TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position = "H") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with different values of $L$,  $\mu=1$ and \(\widetilde{H}_{\text{AO}}\) estimator. 
In all cases, the nominal level was achieved. 
We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, $\alpha=-2$, and \(\widetilde{H}_{\text{AO}}\) estimator.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.
<!-- ACF Please clarify which alternatives you used for the power -->
<!-- JA Corrected -->

@@

  return(p_value < alpha_nominal)  
}
R <- 1000
mu <- 1
B <- 100
L_values <- c( 3, 5, 8, 11)
sample_sizes <- c( 25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results <- data.frame()
for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

@@

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

@@

        for (r in 1:R) {
          z <- gi0_sample(mu, -2, L, s)
          TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
          #TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        }

@@

  return(results)
}
R <- 1000
mu <- 1
L_values <- c(3, 5,  8, 11)
B <- 100
sample_sizes <- c(25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")
```

@@

The AIC and BIC results in Tables&nbsp;\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian} indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different distributed Gamma and \(G_I^0\) synthetic sample sizes match the properties of an LN distribution.
It is important to note that this conclusion was drawn empirically based on a dictionary of distributions that are analytically tractable and well-defined under biparametric, unimodal, asymmetric, and positive distributions.

<!-- \textcolor{red}{% -->
<!-- ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião. Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica. Uma alternativa empírica para uma solução do momento usando distribuições mais desenvolvidas na literatura e que sejam analiticamente tratáveis. Estou pensando corretamente? Se sim, por que não log-t-student, log-Laplace, power exponential, Log-hyperbolic,.... (e a lista segue). Sugiro talvez indicar (i) a dedução da distribuição assintótica das estatísticas em função de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro. Do que eu entendi, a suposição da normal assintótica para entropia vem de uma coleção de trabalhos teóricos. Já a LN, do que percebi, não. Coloquei um comentário em verde. Vejam se estão de acordo. -->
<!-- } -->

@@

# Graficar las comparaciones
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

The three test statistics (entropy-based, ${\text{CV}}$, and ${\text{CV}_{\text{MnAD}}}$) are applied to the simulated image using local sliding windows of size $7\times 7$, as shown in Figures&nbsp;\ref{fig:sim_results}(a)--(c). 
For the first test we considered the \(\widetilde{H}_{\text{AO}}\)  estimator due to its superior performance in simulations and shorter processing time compared to other entropy estimators.
